Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows

### 2017-03-01 paper.tex
make sentences on each line

\title[An \textsf{achemso} demo]
  {Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows}

@@

The final search with the augmented database is conducted with notches: the final notch search is specific to each dataset: we only recommend including the common missed monoisotopic mass values in the final search, the effect of using these notches is shown in Table~\ref{tab:table2}.

>>>>

\title[Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows]
  {Rapid and Accurate Global PTM Discovery (G-PTM-D) Using Post-Acquisition Spectral Calibration and Defined Mass Windows}

@@

The final search with the augmented database is conducted with notches: we only recommend including the common missed monoisotopic mass values in the final search,.
The effect of using these notches is shown in Table~\ref{tab:table2}.
